Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-10 write-ups/PLDI/paper.tex
Fix.
Started to add references.

\section{The GPUs we Tested}

@@

\section{Determining Representative Workloads}

@@

\section{The Overhad of Moving to Cooperative Kernels}

@@

\section{Performance and Responsiveness of Cooperative Scheduling}

@@

@@

>>>>

\subsection{The GPUs we Tested}

@@

\subsection{Determining Representative Workloads}

@@

\subsection{The Overhad of Moving to Cooperative Kernels}

@@

\subsection{Performance and Responsiveness of Cooperative Scheduling}

@@

\cite{DBLP:conf/ics/WuCLSV15} \ADComment{Basic idea: map tasks to
  SMs, not to workgroups, so that tasks taht would benefit from being
  processed by the same SM can be scheduled to the same SM.  Has
  little to do with preemption, but more to do with irregular
  computation.}

\cite{DBLP:conf/isca/TanasicGCRNV14} \ADComment{I have not read, but
  it's about enabling preemptive multiprogramming, so we should read
  it carefully.}

\cite{DBLP:conf/ppopp/Muyan-OzcelikO16} \ADComment{I have not read; we
  should understand this one carefully.}

\cite{DBLP:conf/asplos/ParkPM15} \ADComment{Investigates how one might
  implement preemption, i.e.\ shows that it can be achieved.
  Simulator only preemption.  Not sure whether their approach would
  give fair scheduling.}

\cite{DBLP:journals/tog/SteinbergerKBKDS14} \ADComment{Shows how to
  keep a GPU busy by flooding it with work.  Would absolutely not
  stand up to preemption.}

\cite{DBLP:conf/usenix/KatoLRI11} \ADComment{Idea seems to be to
  accept that GPUs do not offer epreemption, but find a reasonable way
  to schedule tasks to maximise responsiveness or throughput.}

@@

\clearpage

\bibliographystyle{abbrvnat}
\bibliography{tyler}
